Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-09 paper.tex
Write "Direct Interaction" section; stub out figures.

\section{A Lesson from Nell}

@@

As illustrated in figure~\ref{fig:nell}, Nell's characters are
always-available agents running on top of a particular system \textit{activity}
(application) which provides specialized functionality.  The agents
are not always foregrounded: constructionist learning occurs when the
child plays freely to ``make things'' with the base activity.
The handwriting tutor is fundamentally a drawing activity; the
adventure involving the magical musical lock is also a music-making activity.
%  ``Making things'' is the key to constructionist learning.
The narrative system is
hooked into each activity to provide passive guidance
(congratulating the child when it notices they've drawn a letter),
active guidance (Apple-Guide--style~\cite{powers:appleguide}
contextual help), or system services (switch activities; jump into a
related story module/lesson plan).

@@

The Nell system is tied to its implementation on a tablet computer.

It's no accident that the Nell system is instantiated on a tablet.

The constructionist learning philosophy seeks to engage kids by
``making things''.  We believe that the direct interaction afforded by
tablet computing helps approach that goal.

Nell is deployed on a tablet computer, and...

Nell's implementation on a tablet computer advances...

\textbf{XXX}

>>>>

\section{A Lesson from Nell}
\begin{figure}
\centering
\epsfig{file=roger1.eps, height=1.5in} % width=3.2in
\caption{Illustration of Nell's primary interface.}\label{fig:nell}
\end{figure}

@@

As illustrated in figure~\ref{fig:nell}, Nell's characters are
always-available agents layered above a particular system \textit{activity}
(application) which provides specialized functionality.  The agents
are not always foregrounded: constructionist learning occurs when the
child plays freely to ``make things'' with the base activity.
The handwriting tutor is fundamentally a drawing activity; the
adventure involving the magical musical lock is also a music-making activity.
%  ``Making things'' is the key to constructionist learning.
The narrative system is
hooked into each activity to provide passive guidance
(congratulating the child when it notices they've drawn a letter),
active guidance (Apple-Guide--style~\cite{powers:appleguide}
contextual help), or system services (switch activities; jump into a
related story module/lesson plan).

@@

\begin{figure}
\centering
\epsfig{file=xo3-3.eps, width=3.2in}
\caption{Nell's solar-powered hardware platform.  The tablet design
  allows for direct interaction.}\label{fig:xo3}
\end{figure}

The constructionist learning philosophy emphasizes creation and
tangible interaction.  Nell uses direct interaction on a tablet
computer to maintain the child's connection to their work
(Figure~\ref{fig:xo3}).

The direct interaction model lowers the floor by eliminating the need
to learn an abstract touchpad or mouse interface.  It also supports
our literacy goals by allowing direct handwriting instruction and the
use of handwriting as an interface.
